---
title: "Data 607 Final Project"
author: "Matthew Roland, Jean Jimenez, Kelly Eng"
date: "2023-12-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rio)
library(tidyverse)
library(mongolite)
library(googlesheets4)
library(flextable)
library(cluster)
library(factoextra)
```

# Clustering of

## Importing the Data

We stored the European survey data on MongoDB because it was too large. A MongoDB database was constructed and data was imported to it. Afterwards, a connection was established to a MongoDB server, specifying the database and collection to be accessed.

We defined a specific set of columns to be retrieved. This was done by creating a vector of column names, which are fields within the MongoDB collection. These fields represent different attributes or questions from the survey data.

After defining the columns, a MongoDB projection query is constructed. This projection is a way to specify which fields in the documents should be included in the returned data. In this case, the query is set up to retrieve only the specific columns.

```{r}
connection_string <- "mongodb+srv://teamandroid:O9sWUq5h7JMDioFk@cluster0.kk0rkpj.mongodb.net/"
collection <- mongo(collection="european_values", db="database", url=connection_string)

columns <- c("study", "wave", "uniqid", "year", "cntry_AN", "A001", "A002", "A003", "A004", "A005", "A006", "A008", "A170", "A040", "A065", "A066", "A068", "A165", "B008", "D001_B", "G007_35_B", "Y002", "E015", "E035", "E036", "E039", "E069_01", "E225", "F025", "F028", "F028B_WVS7", "F066_EVS5", "F034", "F050", "F051", "F053", "F054", "F063", "X001", "X003R", "G027A", "X007", "X011", "X013", "X025A_01", "X028", "X047_WVS7", "X047E_EVS5", "C002", "G052")

#giturl <- "https://github.com/Mattr5541/DATA_607_Final_Project/raw/main/EVS_WVS_Joint_rData_v4_0.rdata"

#data <- import(giturl)

projection <- paste0('{', paste0('"', columns, '": 1', collapse = ','), '}')
data <- collection$find(query = '{}', fields = projection)
```

### Importing Eurovision Dataset

We imported the eurovision datasets two ways. Originally, the data was intended to be imported from a Google Sheet using the `read_sheet` function. This approach would have allowed for a direct import of data from a Google Sheet specified by its ID, likely making use of a package like `googlesheets4` in R, which facilitates such operations. The specific sheet titled "All Songs Ever" from the Eurovision dataset was targeted.

However, due to difficulties in accessing the Google Sheet among the group group, an alternative method was adopted. The data was instead placed on GitHub.

```{r}
##Google Drive Attmept
#eurovision_id="1jRFrSEQaLmYSFLujaaEMEE33rNUo0UMOlLGXngqaYLQ"
#eurovis_raw=read_sheet(eurovision_id, sheet="All Songs Ever")


eurogit <- "https://raw.githubusercontent.com/Mattr5541/DATA_607_Final_Project/main/Copy_of_Every_Eurovision_Result_Ever%20-%20All%20Songs%20Ever.csv"
eurovis_raw <- import(eurogit)
```

## Preprocessing the Data

From the European survey data, we selected many variables. These variables cover a wide range of topics, such as country abbreviations, various life values (like family, friends, work, religion), happiness and life satisfaction, religious and political affiliations, trust levels in different entities, demographic information, and socio-economic indicators.

Afterwards we filtered the data and applied regional classification. The classification divides the countries into regions like Western Europe and Southern Europe. We also dropped NA values.

```{r}
#Selecting our variables of interest (go over this in case you want to add more variables or remove any more); also, I may try to integrate these changes into MongoDb, but that remains to be seen
#Some notes: Only waves 5 & 7 are integrated into this dataset; wave 5 refers to the EVS data and wave 7 refers to the WVS data; we may need to keep this in mind when we filter data and plan our analyses

##Here are the variables I chose to include: cntry_AN = abbreviated names for countries; A001 = Important in Life: Family; A002 = Important in Life: Friends; A003 = Important in Life: Leisure Time; A004 = Important in Life: Politics; A005 = Important in Life: Work; A006 = Important in Life: Religion; A008 = Feeling of happiness; A170 = Satisfaction with your life; A040 = Important child qualities: religious faith; A065 = Member: Belong to religious organization; A066 = belong to education, arts, music, or cultural activities; A068 = Belong to political parties; A165 = Most people can be trusted; B008 = Protecting environment vs. economic growth; ; D001_B = Trust your family; G007_35_B = Trust: People of another religion; Y002 = Post-Materialist Index Score; E015 = Future changes: Less importance placed on work; E035 = Income inequality; E036 = Private vs State ownership of business; E039 = Competition good or harmful; E069_01 = Confidence: Churches; E225: Democracy: Religious authorities interpret the laws; F025 = Religious denomination; F028 = How often do you attend religious services; F028B_WVS7 = How often do you pray; F066_EVS5 = Pray to God outside of religious services; F034 = Religious person; F050 = Believe in God; F051 = Believe in: life after death; F053 = Believe in: hell; F054 - Believe in: heaven; F063 - How important is God in your life; X001 - Sex; X003R - Age recoded (6 intervals); G027A - Respondent immigrant / born in country; X007 - Marital status; X011 - How many children do you have; X013 - Number of people in household; X025A_01 - Highest educational level attained; X028 - Employment status Respondent; X047_WVS7 - Scale of incomes (WVS7); X047E_EVS5 - Scale of incomes (EVS5); C002 - Jobs scarce: Employers should give priority to (nation) people than immigrants; G052 - Evaluate the impact of immigrants on the development of [your country]

ews <- data[, !names(data) %in% "_id"]

#Belgium, Liechtenstein, Luxembourg, Monaco, Malta, San Marino were not included in the dataset; Note: CH denotes Switzerland; HR denotes Croatia
#Regions were defined in accordance with UN geoscheme classification (although I decided to add in Great Britain to Western Europe, following the CIA classification system, just as a matter of convenience. Let me know if there's a better way to go about this)
ews <- ews %>% filter(cntry_AN %in% c("AT", "FR", "DE", "NL", "CH", "GB", "AL", "AD", "BA", "HR", "CY", "GR", "IT", "ME", "MK", "PT", "RS", "SI", "ES", "US"))

ews <- ews %>% mutate(region = ifelse(cntry_AN %in% c("AT", "FR", "DE", "NL", "CH", "GB"), "Western Europe", "Southern Europe"))

ews <- ews %>% mutate(region = if_else(cntry_AN == "US", "America", region))

##And now I can clean the data
#First, I'll start by removing all values that denote a participant's uncertainty or refusal to answer question items; Items coded -1 -- -5 are considered missing, or instances in which the participant did not answer; -4 represents instances in which the question was not included in the survey (i.e., the question was included in the EVS survey, but not the EWS survey. As a result, I will keep it in for now, since its removal will lead to too much systematic data loss; we can handle those situations by simply excluding wave 5 or 7 from certain analyses/graphs)
ews <- ews %>% mutate_all(~ ifelse(. %in% c(-1, -2, -3, -5), NA, .))
ews <- drop_na(ews)
```

### Preprocessing Eurovision Data

From the eurovision data set, I created `semiclean_eurovis`. This subset focuses on specific columns: Country, Year, Language, Grand Final Points, and Grand Final Place. I filtered the data to include only the years from 2017 to 2022, focusing on Eurovision contests that correspond to the survey years.

I then process the different languages the songs are in to extract first language. I then classify them by language type.

```{r}
#names(eurovis_raw)


semiclean_eurovis = eurovis_raw %>%
  select(Country, Year, Language, `Grand Final Points`,`Grand Final Place`) %>%
  filter(Year >= 2017, Year <= 2022)

semiclean_eurovis$`Grand Final Points`=as.numeric(unlist(semiclean_eurovis$`Grand Final Points`))

semiclean_eurovis$`Grand Final Place`=as.numeric(unlist(semiclean_eurovis$`Grand Final Place`))

names(semiclean_eurovis)=c("country","year","lang","pts","place")


#unique(semiclean_eurovis$lang)

sce1=semiclean_eurovis %>%
  mutate(first_lang=strsplit(lang, split=',')) %>%
  unnest(first_lang) %>%
  select(country, year, first_lang, pts,  place)


#turning Lang into Factor

clean_eurovis=sce1 %>%
  filter(complete.cases(.)) %>%
  mutate(language_category = case_when(
    first_lang %in%  c("Portuguese", "Italian", "French", " French","Spanish"," Italian") ~1,
    first_lang %in% c("English", "Icelandic"," Srnán Tongo"," English") ~2,
   first_lang %in%  c("Russian","Serbian", "Belarusian","Ukrainian","Slovene") ~3,
   first_lang %in%  c("Hungarian","Northern Sami"," Northern Sami") ~ 4,
    first_lang == "Albanian" ~ 5))

clean_eurovis=clean_eurovis %>%
  select(country, year, language_category, pts, place)

```

## Initial Data Visualization and Exploration

### Eurovision Data

I created `most_gsb`, which targets countries that have won the top three places (first, second, or third) in each year of the contest. This is done through grouping the data by year, filtering to include only the top three places, and then re-grouping by country to count the total number of top-three finishes for each country.

After this grouping and filtering, the data is summarized to count the number of times each country has appeared in the top three places during the specified years. This summary is then arranged in descending order to highlight the countries with the most medals.

The next step involves creating a table visualization using the `flextable` package. The `flextable` function transforms the `most_gsb` data into a more visually appealing and understandable table format. The column names are made more descriptive: 'country' is relabeled as 'Nation' and 'count' as 'Number of Eurovision Medals'. This makes the table easier to interpret for readers.

Furthermore, an additional header row is added to the table to provide a clear title: "Table of Eurovision Medals by Country 2017-2022". This title contextualizes the table, indicating its content and the timeframe it covers.

`ft_gsb2`, is a well-structured and informative table that visually represents the countries with the most top-three finishes in the Eurovision song contest over the specified years. This visualization is a useful tool for quickly understanding which countries have been most successful in recent Eurovisions, highlighting patterns and trends in the contest's outcomes.

```{r}
#Visualizing Countries with most Gold, Silver, and bronze medals

most_gsb=semiclean_eurovis %>%
  group_by(year) %>%
  filter(place==1| place ==2| place == 3) %>%
  ungroup()%>%
  group_by(country)%>%
  summarise(count = n()) %>%
  arrange(desc(count))

ft_gsb1= flextable(most_gsb)

ft_gsb2 = ft_gsb1 |> 
  set_header_labels(country = "Nation", count = "Number of Eurovision Medals")  |>
  add_header_row(values = "Table of Eurovison Medals by Country 2017-2022", colwidths = 2) 

ft_gsb2
  
```

After extracting the primary language, the data is regrouped by this first language and summarized to count the number of songs performed in each language. This summarization helps us see the frequency of each language's use in the contest. The results are arranged in descending order to highlight the most common languages.

The `flextable` package is again used to create a visually appealing table, `langs`, representing this language distribution data. The table's headers are renamed for clarity, and an explanatory header row is added, providing context to the table.

In addition to the table, a histogram is created using the `ggplot2`. This histogram, `eurolang_hist`, visualizes the same language distribution data.

```{r}
#Visualizing Language Distributions

eurovis_langs= semiclean_eurovis %>%
  group_by(lang) %>%
  mutate(first_lang=sapply(strsplit(lang, ", "), `[`, 1)) %>%
  ungroup()%>%
  group_by(first_lang) %>%
  summarise(count=n()) %>%
  arrange(desc(count))

total_songs=eurovis_langs %>%
  summarise(result=sum(count))

langs=flextable(eurovis_langs)|> 
  set_header_labels(first_lang = "Song Performed First Language", count = "Number")  |>
  add_header_row(values = "Table of Eurovison Song First Language", colwidths = 2)

langs

eurolang_hist=ggplot(eurovis_langs, aes(x = first_lang, y = count)) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_minimal() +
  labs(x = "Language", y = "Count", title = "Histogram of Eurovision Song First Language 2017-2022") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

eurolang_hist

```

This step calculates the total points each language has garnered in top positions across the specified years.

The results are then visualized in two ways. First, a table named `lang_pt_tbl` is created using the `flextable` package. Second, a histogram is generated using the `ggplot2` package.

```{r}
#Determining Winning Languages pts

lang_pts=semiclean_eurovis %>%
  group_by(year) %>%
  filter(place==1| place ==2| place == 3) %>%
  ungroup()%>%
  group_by(lang) %>%
  mutate(first_lang=sapply(strsplit(lang, ", "), `[`, 1)) %>%
  ungroup()%>%
  group_by(first_lang) %>%
  summarise(agg_pts=sum(pts, na.rm= TRUE))

lang_pt_tbl=flextable(lang_pts)|> 
  set_header_labels(first_lang = "Song Performed First Language", agg_pts = "Aggregated Points")  |>
  add_header_row(values = "Table of Eurovision 1st, 2nd, or 3rd Place Points by Language 2017-2022", colwidths = 2)

lang_pt_tbl


lang_pts_hist=ggplot(lang_pts, aes(x = first_lang, y = agg_pts)) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_minimal() +
  labs(x = "Language", y = "Aggregated Points", title = "Histogram of Eurovision 1st, 2nd, or 3rd Place Points by Language 2017-2022") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

lang_pts_hist


```

The dataset is grouped by both year and the first language, to observe the distribution of languages across different years. A summary is created for each language and year, counting the number of times each language appeared in the top three positions.

```{r}
#Visualizing time distribution of Languages
lang_time=semiclean_eurovis %>%
  group_by(year) %>%
  filter(place==1| place ==2| place == 3) %>%
  ungroup()%>%
  group_by(lang) %>%
  mutate(first_lang=sapply(strsplit(lang, ", "), `[`, 1)) %>%
  ungroup()%>%
  group_by(year, first_lang) %>%
  summarise(count = n(), .groups = 'drop') %>%
  arrange(year, desc(count))


lang_time_tbl=flextable(lang_time)|> 
  set_header_labels(year="Year", first_lang = "Song Performed First Language", count = "Count")  |>
  add_header_row(values = "Table of Eurovision 1st, 2nd, or 3rd Place Points by Language and Year 2017-2022", colwidths = 3)

lang_time_tbl

```

The data is grouped by country. For each country, the total points ( 'pts') accumulated over the specified years are aggregated. This is done using the `sum` function, with the `na.rm = TRUE` parameter to ensure that missing values do not affect the calculation. T

To visualize this data, two methods are used: a table and a histogram.

```{r}
#Visualizing Point Distributions by Country
eurovis_pts= semiclean_eurovis %>%
  group_by(country) %>%
  summarise(agg_pts=sum(pts, na.rm= TRUE)) %>%
  arrange(desc(agg_pts))


pts_tab=flextable(eurovis_pts)|> 
  set_header_labels(country = "Country", agg_pts = "Aggregated Eurovision Points")  |>
  add_header_row(values = "Table of Aggregated Eurovison Points by Country 2017-2022", colwidths = 2)

pts_tab

europts_hist=ggplot(eurovis_pts, aes(x = country, y = agg_pts)) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_minimal() +
  labs(x = "Country", y = "Total Points", title = "Histogram of Aggregated Eurovision Points by Country 2017-2022") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

europts_hist
```

## Data Processing

### Creating a Modified Data set Representing Mean Values by Country

We use `mutate` to rename a series of survey question codes (like A001, A002, etc.) to more descriptive variable names. This renaming makes the dataset more interpretable and user-friendly. For instance, 'A001' is renamed to 'Family', 'A002' to 'Friends', and so on, covering a wide range of topics like leisure, politics, work, religion, happiness, life satisfaction, and various other aspects related to personal beliefs, social trust, and environmental attitudes.

After these transformations, the `select` function is applied. This function is used to pick out only the relevant variables from the dataset.

```{r}
#ews_group <- ews %>% group_by(year,cntry_AN ) %>% summarize(Family = mean(A001#), Friends = mean(A002), Leisure = mean(A003), Politics = mean(A004), Work = #mean(A005), Religion = mean(A006), Happiness = mean(A008), Satisfaction = #mean#(A170), Religious_Children = mean(A040), Organized_Religion = mean(A065), #Cultural_Activities = mean(A066), Political_Party_Affiliation = mean(A068), #Trust_People = mean(A165), Protect_Environment_vs_Economy = mean(B008), #Trust_Family = mean(D001_B), Trust_Religion = mean(G007_35_B), Materialism = #mean(Y002), Future_Change_Less_Work = mean(E015), Income_Inequality = mean#(E035), Business_Ownership = mean(E036), Competition = mean(E039), #Confidence_Church = mean(E069_01), Democracy_Religion = mean(E225), #Deonomnation = mean(F025), Religious_Service_Attendance = mean(F025), Pray = #mean(F028B_WVS7), Pray_Outside_Service = mean(F066_EVS5), Religious = mean#(F034), Belivie_in_God = mean(F050), Belive_in_Afterlife = mean(F051), #Belive_in_Hell = mean(F053), Believe_in_Heaven = mean(F054), #Job_Priority_to_Immigrants = mean(C002), Impact_of_Immigration = mean(G052))





ews_group <- ews  %>% mutate(Family =A001, Friends = A002, Leisure = A003, Politics = A004, Work = A005, Religion = A006, Happiness = A008, Satisfaction = A170, Religious_Children = A040, Organized_Religion = A065, Cultural_Activities =A066, Political_Party_Affiliation = A068, Trust_People = A165, Protect_Environment_vs_Economy = B008, Trust_Family = D001_B, Trust_Religion = G007_35_B, Materialism = Y002, Future_Change_Less_Work =E015, Income_Inequality = E035, Business_Ownership = E036, Competition = E039, Confidence_Church = E069_01, Democracy_Religion = E225, Deonomnation = F025, Religious_Service_Attendance = F025, Pray = F028B_WVS7, Pray_Outside_Service = F066_EVS5, Religious = F034, Belivie_in_God = F050, Belive_in_Afterlife = F051, Belive_in_Hell = F053, Believe_in_Heaven = F054, Job_Priority_to_Immigrants = C002, Impact_of_Immigration = G052) %>%
   select(cntry_AN, year, Family , Friends , Leisure, Politics , Work, Religion , Happiness , Satisfaction , Religious_Children , Organized_Religion , Cultural_Activities , Political_Party_Affiliation , Trust_People , Protect_Environment_vs_Economy, Trust_Family , Trust_Religion , Materialism , Future_Change_Less_Work , Income_Inequality , Business_Ownership , Competition , Confidence_Church, Democracy_Religion , Deonomnation, Religious_Service_Attendance , Pray , Pray_Outside_Service, Religious , Belivie_in_God , Belive_in_Afterlife , Belive_in_Hell, Believe_in_Heaven, Job_Priority_to_Immigrants , Impact_of_Immigration )
```

### Adding Country Code to Eurovision Dataset

Here, I merge two datasets, one containing Eurovision data and another with country codes.

The purpose of this operation is to combine the Eurovision data with a standardized set of country codes, which is necessary to link it with our other data.

```{r}

country_key=read.csv(url("https://gist.githubusercontent.com/tadast/8827699/raw/f5cac3d42d16b78348610fc4ec301e9234f82821/countries_codes_and_coordinates.csv"))

country_key=country_key %>%
  select(Country, Alpha.2.code)

names(country_key)=c("country","cntry_AN")

eurovis_w_cc=clean_eurovis %>%
  right_join(country_key, by="country")


```

### Merging Eurovision Data and Survey Data

```{r}


# Checking column names and types in ews_group
#print(names(ews_group))
#str(ews_group)

# Checking column names and types in eurovis_w_cc
#print(names(eurovis_w_cc))
#str(eurovis_w_cc)

ews_group$year = as.integer(ews_group$year)
eurovis_w_cc$year = as.integer(eurovis_w_cc$year)


# Trim leading and trailing spaces in cntry_AN of eurovis_w_cc
eurovis_w_cc$cntry_AN <- trimws(eurovis_w_cc$cntry_AN)


joint_data = inner_join(ews_group, eurovis_w_cc, by = c("cntry_AN", "year"))



joint_data$language_category=as.integer(joint_data$language_category)


joint_data=joint_data%>%
  ungroup()%>%
  filter(complete.cases(.)) %>%
  select(-cntry_AN)

#Alright, so character variables do not work with k-means clustering, so I have two options: 1) exclude country from the analysis entirely; 2) find the means for each country so that way, each instance of country is unique and can be used as an identifier (I think year will need to be excluded entirely)

joint_data_mean <- joint_data %>% group_by(country) %>% summarize(Family = mean(Family), Friends = mean(Friends), Leisure = mean(Leisure), Politics = mean(Politics), Work = mean(Work), Religion = mean(Religion), Happiness = mean(Happiness), Satisfaction = mean(Satisfaction), Religious_Children = mean(Religious_Children), Organized_Religion = mean(Organized_Religion), Cultural_Activities = mean(Cultural_Activities), Political_Party_Affiliation = mean(Political_Party_Affiliation), Trust_People = mean(Trust_People), Protect_Environment_vs_Economy = mean(Protect_Environment_vs_Economy), Trust_Family = mean(Trust_Family), Trust_Religion = mean(Trust_Religion), Materialism = mean(Materialism), Future_Change_Less_Work = mean(Future_Change_Less_Work), Income_Inequality = mean(Income_Inequality), Business_Ownership = mean(Business_Ownership), Competition = mean(Competition), Confidence_Church = mean(Confidence_Church), Democracy_Religion = mean(Democracy_Religion), Deonomnation = mean(Deonomnation), Religious_Service_Attendance = mean(Religious_Service_Attendance), Pray = mean(Pray), Pray_Outside_Service = mean(Pray_Outside_Service), Religious = mean(Religious), Belivie_in_God = mean(Belivie_in_God), Belive_in_Afterlife = mean(Belive_in_Afterlife), Belive_in_Hell = mean(Belive_in_Hell), Believe_in_Heaven = mean(Believe_in_Heaven), Job_Priority_to_Immigrants = mean(Job_Priority_to_Immigrants), Impact_of_Immigration = mean(Impact_of_Immigration), language_category = mean(language_category), pts = mean(pts), place = mean(place))

joint_data_mean <- joint_data_mean %>% column_to_rownames(var = "country")
```

### Standardization

Doing

$$
X_{\text{standardized}} = \frac{X - \mu}{\sigma}
$$

```{r}
#stand_jointdf = joint_data %>%
  #mutate(across(-c(year, country), ~ (scale(.))))

stand_jointdf = joint_data_mean %>% scale()
```

### Performing K-Means Clustering on the Standardized Dataset

```{r}

#stand_jointdf_mod <- stand_jointdf %>% select(-c(country))

#stand_jointdf_mod <- stand_jointdf
  
k_means_results <- kmeans(stand_jointdf, centers = 2, nstart = 25)
str(k_means_results)
print(k_means_results$centers)  # Cluster centroids
print(k_means_results$size)     # Size of each cluster

#Now I will use a function to calculate the optimal k value for this analysis
set.seed(123)
wss <- function(k) {
  kmeans(stand_jointdf, k, nstart = 25)$tot.withinss
}

k_values <- 1:10

wss_values <- map_dbl(k_values, wss)

plot(k_values, wss_values,
       type="b", pch = 19, frame = FALSE, 
       xlab="Number of clusters K",
       ylab="Total within-clusters sum of squares")

## Based on the "bend" in the graph, 4 may be a more optimal choice for our k

final <- kmeans(stand_jointdf, centers = 4, nstart = 25)
print(final)

fviz_cluster(final, data = stand_jointdf)
```

With that, we are left with four clusters, wherein cluster 1 contains observations for Albania; cluster 2 contains observations for Croatia and Italy; cluster 3 contains observations for Serbia, Cyprus, and Greece; Cluster 4 contains observations for Austria, Germany, the Netherlands, Spain, France, and the United Kingdom

```{r}
joint_data_cluster <- joint_data_mean %>% mutate(Cluster = final$cluster) %>% group_by(Cluster) %>% summarize(pts = mean(pts), place = mean(place))

flextable(joint_data_cluster)

joint_data_cluster %>% ggplot(aes(Cluster, pts)) + geom_bar(stat = "identity", fill = "blue") + ggtitle("Mean Points Earned by Cluster") + ylab("Points")

```

Based on this descriptive cluster analysis, it would seem that countries in the second cluster (Croatia and Italy) are more likely to score the highest number of points, and thus, place higher

### Resources

<https://uc-r.github.io/kmeans_clustering#>:\~:text=clustering%20algorithms%20%26%20visualization-,Data%20Preparation,scaled)%20to%20make%20variables%20comparable.
